### 2016-08-23 notions.tex
cheers

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.

@@

We should be able to show
\begin{itemize}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\end{itemize}

>>>>

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness
game, in which the adversary seeks to return an element of the
represented set~$S$.  The final notion is reminiscent of
semantic-security for encryption schemes, and attempts to capture the
intuition that the representation~$M$ and the public
information~$\pubaux$ should not leak any efficiently computable
information about~$S$.

\tsnote{flesh out}

@@

\todo{We should be able to show...}
\begin{itemize}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\end{itemize}
